Starcode: sequence clustering based on all-pairs search

### 2014-11-04 doc/document.tex
Working on the discussion (in progress).

Since no sequencing technology has an error rate higher than 20\%,
it is expected that sequences appearing from sequencing errors will
always have 5 times or lower read count than the canonical sequence.
Otherwise, sequences are more likely unrelated, or both derived from
the same canonical sequence.

For other sequence clustering problems, starcode implements a
multi-purpose algorithm called ``sphere clustering''
\citep{pmid23953119}. In sphere clustering, sequences are sorted by
frequency of occurrence. Starting from the most
frequent, each sequence becomes canonical and claims all its
$\tau$-matches, which forms a cluster of radius $\tau$ (hence the
name). Claimed sequences are immediately removed, so that they can
belong to only one cluster.

@@

\begin{table}[h]
\centering
\caption{Software execution options used in simulation benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{execution options}\\
    \hline
    starcode & \texttt{starcode -d3}\\
    slidesort & \texttt{slidesort\_v2 -d 3 -t E -c DNA}\\
    CD-HIT 4.6.1 & \texttt{cd-hit-est -n 9 -c 0.9 -M 0 -r 0}\\
    SEED & \texttt{SEED --mismatch 3}\\
\end{tabular}
%}
\label{tab:params1}
\end{table}

\begin{table}[h]
\centering
\caption{Software execution options used in real data benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{execution options}\\
    \hline
    starcode & \texttt{starcode -d3}\\ 
    slidesort & \texttt{slidesort\_v2 -d 3 -u -t E -c DNA}\\
    CD-HIT 4.6.1 & \texttt{cd-hit-est -n 8 -c 0.94 -M 0}\\
    SEED & \texttt{SEED --mismatch 3 --shift 3}\\ 
\end{tabular}
%}
\label{tab:params2}
\end{table}

\subsection{Presentation and basic performance}
\label{performance}
Starcode is a general purpose DNA sequence clustering tool with a
strong focus on error correction. Errors are assumed to be mismatches,
insertions or deletions (the implementation presented here matches
sequences with up to 8 errors). The input sequences can be single
or paired-end reads, with an upper limit of 1024 nucleotides (512
for paired-end). Sequences may be of variable length, they may
be trimmed and filtered for quality or not. Input formats may be raw
sequence, fasta or fastq (in which case starcode ignores the quality).
By default, starcode outputs sequence clusters, it can also be used
to filter out redundant sequences from input files. By default,
clustering is performed under the assumption that divergence occurs
from experimental errors (sequencing errors, PCR mutations
\textit{etc}), a more general algorithm is also available for other
clustering problems (an example of which is given in section
\ref{section:motifs}).

@@

\subsection{Benchmark}
\label{section:benchmark}
We benchmarked starcode against the sequence clustering algorithms
slidesort \citep{pmid21148542}, seed \citep{pmid21810899},
rainbow \citep{pmid22942077} and cd-hit \citep{pmid23060610}. Even though
slidesort is an all-pairs search algorithm, it was included in the
benchmark because sequence comparison is the most computationally
intensive step of the sequence clustering problem. Rainbow runs
exclusively on paired-end reads, while the other tools run on single
reads.

%% Synthetic data %%
The performance of sequence clustering algorithms can be sensitive
to the size of the clusters in the dataset, which in many applications
is not known \textit{a priori}. We therefore set up a benchmark on
artificial datasets to test the accuracy and the scaling of the
tools on a known cluster structure. We generated 4 datasets of 1 million
50-mers arranged in 1 to 1,000 clusters. Each cluster consisted
of 100 repeats of the same centroid sequence, plus satellites
derived from the centroid by incorporating 3 errors including at
most 1 indel. The number of satellites per cluster ranged from
999900 to 900. Evaluating the exactness of slidesort on these datasets
was problematic because the number of 3-matches in each dataset is
not known (pairs of statellites in the same cluster may be 3-matches
or not). For this reason we only compared the number of pairs found
by starcode with the number of pairs found by slidesort. The 
outcome of the test is summarized in
Figure \ref{fig:benchmark}.

\begin{figure}[!tpb]
  \centerline{\includegraphics[scale=0.47]{benchmark.pdf}}
\caption{Accuracy of the sequence clustering and all-pairs search
algorithms. Starcode, seed and cd-hit were bencmarked on 4 datasets
with the same number of sequences, but different number of clusters
(see main text). \textbf{a} Starcode identifies the correct number
of clusters, while seed and cd-hit identify about 40 false positives
per true positive. \textbf{b} Slidesort identifies 5-10\% less
pairs than starcode. In both panels, the red line is first
bisector.}
\label{fig:benchmark}
\end{figure}

@@

The running time of the different tools as a function of the size
of the clusters is shown on Figure \ref{fig:benchmark}c. For seed
and cd-hit it decreases as the cluster size increases, whereas
for starcode and slidesort it increases. In spite of this trend,
the performance of starcode remains competitive, even for clusters
of 1 million sequences. The memory usage is shown in Figure
\ref{fig:benchmark}c.
In conclusion, starcode was the only tool to achieve perfect precision
on these datasets. It also maintains competitive performance in
running time and memory usage.

%% Biological datasets %%
The performance on artificial data is not always in agreement with
the performance on experimental datasets. In typical experiments,
the sizes of the clusters may be uneven, and the reads may contain
near constant regions that may degrade the performance.
We benchmarked sequence clustering algorithms on the problem of
clustering TRIP barcodes \citep{pmid23953119}. Briefly, the principle
of TRIP (Thousands of Reporters Integrated in Parallel) is to tag
reporter transcripts with random barcodes and measure the abundance
of barcodes in the RNA as a proxy for gene expression. There is no
reference to match aberrant barcodes against, because the tagging
sequences are unknown.

The basic properties of the datasets used for benchmarking are
summarized in Table~\ref{tab:biobench_properties}. Datasets 1 and 2
consist of Illumina single reads; they differ by the total read count
and by the empirical cluster sizes. According to the output of starcode,
the largest clusters of dataset 1 contain approximately 2,000 sequences,
while dataset 2 contains 4 clusters with more than 1 million sequences.
Dataset 3 consist of Illumina paired-end reads.

@@

The running times of starcode, seed, slidesort, rainbow and cd-hit-est
are summarized in Table~\ref{tab:biobench_runtime}. Starcode was faster
than the other tools on all the datasets. Seed came in second position
on datasets 1 and 2, with a running time approximately 800 and 20 times
greater, respectively. Rainbow came in second position on dataset 3,
but it is the only other tool able cluster paired-end reads. We did not
record the exact running times past 10 days since this is several
orders of magnitude higher than the running time of starcode.

@@

The memory footprint of the different tools on the same datasets is
shown in Table~\ref{tab:biobench_memory}. The values represent the
peak memory usage throughout the run on the datasets described above.
On datasets 1 and 3, starcode had a significantly larger memory usage
than the best tool, while on dataset 2 it used significantly less
memory than seed and approximately as much as cd-hit. A large portion
of the memory usage of starcode is dedicated to the trie structures
used in the poucet search, which explains why starcode is in general
more memory-demanding than alternative tools.

\begin{table}[h]
\centering
\caption{Memory usage (in Gb).}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{dataset 1} &
      \textit{dataset 2} & \textit{dataset 3} \\ \hline
    starcode   & 9.4 & 30.9 & 5.2 \\
    seed       & 4.1 & 53.9 & -   \\
    sidesort   & 1.9 & 13.9 & -   \\
    rainbow    & -   & -  & 0.5   \\
    cd-hit-est & 3.8 & 28.5 & -   \\
\end{tabular}
\label{tab:biobench_memory}
\end{table}

%\subsection{Clustering TRIP barcodes}
%In the course of setting up the TRIP technology in our laboratory
%\citep{pmid23953119}, we realized the need to develop efficient
%algorithms to cluster similar sequences. Briefly, the principle of TRIP
%(Thousands of Reporters Integrated in Parallel) is to tag reporter
%transcripts with random barcodes and measure the abundance of barcodes
%in the RNA as a proxy for gene expression. There is no reference to
%match aberrant barcodes against, because the tagging sequences are
%unknown. Instead, barcodes are matched against each other and clustered
%by similarity to infer canonical sequences.
%
%We tested the efficiency of starcode on the TRIP dataset from
%\cite{pmid23953119}. In the experiment labeled mPGKA, we identified
%24.1 million (91\%) barcode-containing reads out of 26.6 million,
%consisting of approximately 223,000 and 220,000 unique barcode sequences
%for PCR replicates 1 and 2, respectively. Following the authors, we kept
%only the barcodes with at least 5 counts and performed clustering as
%described: ``First we sorted barcodes according to their counts. Then,
%for each barcode (starting from the most frequent one), we identified
%and removed all its mutant versions, defined as barcodes within a Hamming
%distance of 2.'' We implemented this method, here on referred to as the
%``sequential algorithm'' with the function call
%\texttt{stringDist(method='lv', maxDist=2)} from R the package
%\texttt{stringDist} \citep{R}.  When replacing the Hamming distance by
%the Levenshtein
%distance, starcode produced exactly the same output as the sequential
%algorithm. The running time of starcode averaged over the replicates was
%2.90 seconds, \textit{versus} more than 3 minutes 40 seconds, which
%represents a 75-fold speedup.
%
%The performance of the sequential algorithm relies on the arbitrary
%exclusion of reads with less than 5 counts, the main purpose of which
%is to reduce the computational burden. When all barcodes were kept,
%the average running time of starcode was 10.27 seconds, \textit{versus}
%$>$ 6 hours for the sequential algorithm. Using the Hamming distance,
%as the authors originally suggested, decreased the average running time
%of the sequential algorithm to about 3 hours and 30 minutes (and
%the output differed from that of starcode). Note that in all the cases
%mentioned above, starcode was run with a single core to compare the
%algorithms based on similar computer resources. In conclusion, the
%barcode clustering problem can be simplified by various tricks, but
%starcode brings down the running time to nearly instantaneous, and
%thereby obviates the need for such arbitrary heuristics.

\subsection{Identifying enriched sequence motifs}
\label{section:motifs}
Sequence motifs are thought to play an important role in DNA metabolism.
Key regulators, such as transcription factors, nucleosomes and non
coding RNAs have sequence preferences targeting them to the sites where
they act. Identifying those sequences is a way to pinpoint the
regulators and the mechanisms they are involved in. However, the
sequence motifs are not strictly identical at different sites, hence
they are better identified by inexact matching. This problem becomes
computationally difficult for long motifs (above 12-13 nucleotides)
because of the combinatorial scaling. But as motifs become longer, the
problem of identifying abundant inexact matches becomes similar to
barcode clustering. We reasoned that starcode could also be used for
the task of identifying biologically meaningful sequence motifs.

We set up a test based on the meningitis-causing agent
\textit{Neisseria meningitidis}. The genome of this bacterium is
interspersed with a frequent 12 bp sequence known as DNA uptake
sequence \citep{pmid10673000}. We extracted the 12-mers from both
orientations of  the 2.19 Mb genome, yielding 4.39 million 12-mers,
consisting of 2.77 million unique sequences. Clustering the 12-mers
with starcode within a Levenshtein distance of 2 took less than 45
seconds with 12 threads. We identified the known DNA uptake sequence
of \textit{Neisseria meningitidis} (ATGCCGTCTGAA) as the most abundant
12-mer, with 1466 exact and 2096 inexact hits. This result testifies
to the fact that starcode can be used to identify biologically
relevant motifs in bacterial genomes.

To test starcode on another application, we used the RNA-protein
interaction data produced by RNAcompete \citep{pmid19561594}. The
mammalian splicing factor SRSF1 is known to bind RNA GA-rich motifs,
but there is some disagreement about the motif that it recognizes
\citep{pmid23562324}. For each replicate of the human SRSF1 in the
RNAcompete dataset, we replaced the microarray signals by their rank
and extracted the 10-mers from the microarray probes. The 10-mers were
given a score equal to the rank of the probe they belong, and enriched
motifs were found using the sphere clustering of starcode with maximum
Levenshtein distance 2. The score of the most enriched 10-mer is thus
the sum of the ranks of all 10-mers within this distance. Clustering
the 6.3 million extracted 10-mers with 12 threads took about 20 seconds
for each replicate.  The most enriched 10-mers were AGGACACGGA,
AGGACACGGA, AGGACGGAGG, AGGACGGAGG, AGGACACGGA and AGGATACAGG. Except
for the last replicate, the motifs consist of AGGAC and GGA, with a
spacer of variable length. This suggests that the binding of SRSF1 to
RNA may involve a spacer sequence, which would explain the disagreement
between the motifs derived from 6-mers or 7-mers.

\section{Discussion and conclusion}
Through the parallel poucet search algorithm, starcode implements an
exact sequence clustering algorithm that can be faster than popular
heuristics. By design, starcode is tailored to process high throughput
sequencing data on multi-core platforms. Our benchmark shows that
starcode achieves perfect clustering on short random sequences in less
time than what is considered acceptable for heuristic searches. We also
show that starcode outperforms next generation read mappers in this
context. The software tools used for this benchmark are usually not
used for barcode or random sequence clustering. In this respect,
starcode fills a need arising from the development of barcoding
technologies.

>>>>

Since no sequencing technology has an error rate higher than 20\%,
it is expected that sequences appearing from sequencing errors will
always have 5 times or lower read count than the canonical sequence.
Otherwise, sequences are more likely unrelated, or both are derived
from the same canonical sequence.

For other sequence clustering problems, starcode implements a
multi-purpose algorithm called ``sphere clustering''.
In sphere clustering, sequences are sorted by
frequency of occurrence. Starting from the most
frequent, each sequence becomes canonical and claims all its
$\tau$-matches, which forms a cluster of radius $\tau$ (hence the
name). Claimed sequences are immediately removed, so that they can
belong to only one cluster.

\begin{table}[h]
\centering
\caption{Software execution options used in simulation benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{execution options}\\
    \hline
    starcode & \texttt{starcode -d3}\\
    slidesort & \texttt{slidesort\_v2 -d 3 -t E -c DNA}\\
    cd-hit 4.6.1 & \texttt{cd-hit-est -n 9 -c 0.9 -M 0 -r 0}\\
    seed & \texttt{SEED --mismatch 3}\\
\end{tabular}
%}
\label{tab:params1}
\end{table}

\begin{table}[h]
\centering
\caption{Software execution options used in real data benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{execution options}\\
    \hline
    starcode & \texttt{starcode -d3}\\ 
    slidesort & \texttt{slidesort\_v2 -d 3 -u -t E -c DNA}\\
    cd-hit 4.6.1 & \texttt{cd-hit-est -n 8 -c 0.94 -M 0}\\
    seed & \texttt{SEED --mismatch 3 --shift 3}\\ 
\end{tabular}
%}
\label{tab:params2}
\end{table}

@@

\subsection{Presentation and basic performance}
\label{performance}
Starcode is a general purpose DNA sequence clustering tool with a
strong focus on error correction. Errors are assumed to be mismatches,
insertions or deletions (the implementation presented here matches
sequences with up to 8 errors). The input sequences can be single
or paired-end reads, with an upper limit of 1024 nucleotides (512
for paired-end). Sequences may be of variable length, they may
be trimmed and filtered for quality or not. Input formats may be raw
sequence, FASTA or FASTQ (in which case starcode ignores the quality).
By default, starcode outputs sequence clusters, it can also be used
to filter out redundant sequences from input files. By default,
clustering is performed under the assumption that divergence occurs
from experimental errors (sequencing errors, PCR mutations
\textit{etc}.), a more general algorithm is also available for other
clustering problems (an example of which is given in section
\ref{section:motifs}).

@@

\subsection{Benchmark}
\label{section:benchmark}
We benchmarked starcode against the sequence clustering algorithms
slidesort \citep{pmid21148542}, seed \citep{pmid21810899},
rainbow \citep{pmid22942077} and cd-hit \citep{pmid23060610}. Even though
slidesort is an all-pairs search algorithm, it was included in the
benchmark because sequence comparison is the most computationally
intensive step of the sequence clustering problem. Rainbow runs
exclusively on paired-end reads, while the other tools run on single
reads, for this reason all the tools could not be run no the same
dataset.

%% Synthetic data %%
The performance of sequence clustering algorithms can be sensitive
to the size of the clusters in the dataset, which in many applications
is not known \textit{a priori}. We therefore set up a benchmark on
artificial datasets to test the accuracy and the scaling of the
tools on a known cluster structure. We generated 4 datasets of 1 million
50-mers arranged in 1 to 1,000 clusters. Each cluster consisted
of 100 repeats of the same centroid sequence, plus satellites
derived from the centroid by incorporating 3 errors including at
most 1 indel. The number of satellites per cluster ranged from
999900 to 900. Rainbow was not tested on this benchmark because
the generated data is single reads. In addition, evaluating the
exactness of slidesort 
was problematic because the number of 3-matches in each dataset is
not known (pairs of statellites in the same cluster may be 3-matches
or not). For this reason we only compared the number of pairs found
by starcode with the number of pairs found by slidesort. The 
outcome of the test is summarized in
Figure \ref{fig:benchmark}.

\begin{figure}[!tpb]
\centerline{\includegraphics[scale=0.47]{benchmark.pdf}}
\caption{Benchmark results on artificial datasets of known cluster
structure (see main text). \textbf{a} Accuracy measured by the number
of identified clusters. Starcode identifies the correct
number of clusters, while seed and cd-hit identify about 40 false
positives per true positive. The red line is the first bisector and
indicates perfect results. \textbf{b} Accuracy measured by the
number of identified pairs. Slidesort identifies 5-10\% less pairs
than starcode. The red line indicates a ratio of 1. \textbf{c}
Running time of the different tools. As the size of the clusters
the running time of starcode increases but remains competitive.
\textbf{d} Memory usage of the different tools. The memory usage
of starcode decreases as the size of the cluster increases.}
\label{fig:benchmark}
\end{figure}

@@

The running time of the different tools as a function of the size
of the clusters is shown on Figure \ref{fig:benchmark}c. For seed
and cd-hit it decreases as the cluster size increases, whereas
for starcode and slidesort it increases. In spite of this trend,
the performance of starcode remains competitive, even for clusters
of 1 million sequences. The memory usage is shown in Figure
\ref{fig:benchmark}c. The smallest memory footprint is achieved by
slidesort and cd-hit. The memory usage of starcode is the highest
for clusters of size 1000, but it decreases and becomes lower than
the memory usage of seed as the size of the cluster increases.

In conclusion, starcode was the only tool to achieve perfect precision
on these datasets. It also maintains a competitive performance in
terms of running time and memory usage.

%% Biological datasets %%
The performance on artificial data is not always in agreement with
the performance on experimental datasets. Typical experiments present
additional difficulties. For instance,
the sizes of the clusters may be uneven and the reads may contain near
constant regions that may degrade the performance of the algorithm.
We benchmarked sequence clustering algorithms on the problem of
clustering TRIP barcodes \citep{pmid23953119}. Briefly, the principle
of TRIP (Thousands of Reporters Integrated in Parallel) is to tag
reporter transcripts with random barcodes and measure the abundance
of barcodes in the RNA as a proxy for gene expression. There is no
reference to match aberrant barcodes against, because the tagging
sequences are unknown.

The basic properties of the datasets used for benchmarking are
summarized in Table~\ref{tab:biobench_properties}. Datasets 1 and 2
consist of Illumina single reads; they differ by the total read count
and by the empirical cluster sizes. According to the output of starcode,
the largest clusters of dataset 1 contain approximately 2,000 sequences,
while dataset 2 contains 4 clusters with more than 1 million sequences.
Dataset 3 consist of paired-end reads.

@@

The running times of starcode, seed, slidesort, rainbow and cd-hit
are summarized in Table~\ref{tab:biobench_runtime}. Starcode was faster
than the other tools on all the datasets. Seed came in second position
on datasets 1 and 2, with a running time approximately 800 and 20 times
greater, respectively. Rainbow came in second position on dataset 3,
but it is the only other tool able to cluster paired-end reads. We did not
record the exact running times past 10 days since this is several
orders of magnitude higher than the running time of starcode.

@@

The memory footprint of the different tools on the same datasets is
shown in Table~\ref{tab:biobench_memory}. The values represent the
peak memory usage throughout the run on the datasets described above.
On datasets 1 and 3, starcode had a significantly larger memory usage
than the best tool, while on dataset 2 it used significantly less
memory than seed and approximately as much as cd-hit.

\begin{table}[h]
\centering
\caption{Memory usage (in GB).}
\begin{tabular}{l|c c c}
    \textit{software}   & \textit{dataset 1} &
      \textit{dataset 2} & \textit{dataset 3} \\ \hline
    starcode   & 9.4 & 30.9 & 5.2 \\
    seed       & 4.1 & 53.9 & -   \\
    sidesort   & 1.9 & 13.9 & -   \\
    rainbow    & -   & -  & 0.5   \\
    cd-hit-est & 3.8 & 28.5 & -   \\
\end{tabular}
\label{tab:biobench_memory}
\end{table}

\subsection{Identifying enriched sequence motifs}
\label{section:motifs}
As a sequence clustering algorithm, starcode can also be used for
other applications, such as the identification of enriched motifs.
Sequence motifs are thought to play an important role in DNA metabolism.
Key regulators, such as transcription factors, nucleosomes and non
coding RNAs have sequence preferences targeting them to the sites where
they act. Identifying those sequences is a way to pinpoint the
regulators and the mechanisms they are involved in. However, the
sequence motifs are not strictly identical at different sites, hence
they are better identified by inexact matching. This problem becomes
computationally difficult for long motifs (above 12-13 nucleotides)
because of the combinatorial scaling.

%But as motifs become longer, the
%problem of identifying abundant inexact matches becomes similar to
%barcode clustering. We reasoned that starcode could also be used for
%the task of identifying biologically meaningful sequence motifs.

We set up a test based on the meningitis-causing agent
\textit{Neisseria meningitidis}. The genome of this bacterium is
interspersed with a frequent 12 bp sequence known as DNA uptake
sequence \citep{pmid10673000}. We extracted the 12-mers from both
orientations of  the 2.19 Mb genome, yielding 4.39 million 12-mers,
consisting of 2.77 million unique sequences. Clustering the 12-mers
with starcode within a Levenshtein distance of 2,
%took less than 45
%seconds with 12 threads. We identified the known DNA uptake sequence
we identified the known DNA uptake sequence
of \textit{Neisseria meningitidis} (ATGCCGTCTGAA) as the most abundant
12-mer, with 1466 exact and 2096 inexact hits. This result testifies
to the fact that starcode can be used to identify biologically
relevant motifs in bacterial genomes.

To test starcode on another application, we used the RNA-protein
interaction data produced by RNAcompete \citep{pmid19561594}. The
mammalian splicing factor SRSF1 is known to bind RNA GA-rich motifs,
but there is some disagreement about the motif that it recognizes
\citep{pmid23562324}. For each replicate of the human SRSF1 in the
RNAcompete dataset, we replaced the microarray signals by their rank
and extracted the 10-mers from the microarray probes. The 10-mers were
given a score equal to the rank of the probe they belong, and enriched
motifs were found using the sphere clustering of starcode with maximum
Levenshtein distance 2. The score of the most enriched 10-mer is thus
the sum of the ranks of all 10-mers within this distance.
%Clustering
%the 6.3 million extracted 10-mers with 12 threads took about 20 seconds
%for each replicate.  The most enriched 10-mers were AGGACACGGA,
Among the 6 replicates, the most enriched 10-mers were AGGACACGGA,
AGGACACGGA, AGGACGGAGG, AGGACGGAGG, AGGACACGGA and AGGATACAGG. Except
for the last replicate, the motifs consist of AGGAC and GGA, with a
spacer of variable length. This suggests that the binding of SRSF1 to
RNA may involve a spacer sequence, which would explain the disagreement
between the motifs derived from 6-mers or 7-mers.

\section{Discussion and conclusion}
Starocde is a solid algorithm for sequence clustering based on
all-pairs matching. It achieves high precision, and on experimental
datasets it can be faster than popular heuristics. By design,
starcode is tailored to process high throughput sequencing data
on multi-core platforms.
Our benchmark shows that
starcode achieves perfect clustering on short random sequences in less
time than what is considered acceptable for heuristic searches. We also
show that starcode outperforms next generation read mappers in this
context. The software tools used for this benchmark are usually not
used for barcode or random sequence clustering. In this respect,
starcode fills a need arising from the development of barcoding
technologies.
